---
dataMaid: yes
title: Codebook for tidy
date: 2019-05-07 15:16:22
output: word_document
---
```{r , echo=FALSE, include=FALSE, warning=FALSE, message=FALSE, error=FALSE}
library("ggplot2")
library("pander")
```
```{r 'visualFunctions', echo=FALSE, include=FALSE, warning=FALSE, message=FALSE, error=FALSE}
ggAggHist <- getFromNamespace("ggAggHist", "dataMaid")
ggAggBarplot <- getFromNamespace("ggAggBarplot", "dataMaid")
```
# Data report overview
The dataset examined has the following dimensions:


---------------------------------
Feature                    Result
------------------------ --------
Number of observations        180

Number of variables            68
---------------------------------




# Codebook summary table

------------------------------------------------------------------------------------------
Label   Variable                            Class         # unique  Missing  Description  
                                                            values                        
------- ----------------------------------- ----------- ---------- --------- -------------
        **[Subjects]**                      integer             30  0.00 %                

        **[Activity]**                      character            6  0.00 %                

        **[tBodyAcc-mean()-X]**             numeric            180  0.00 %                

        **[tBodyAcc-mean()-Y]**             numeric            180  0.00 %                

        **[tBodyAcc-mean()-Z]**             numeric            180  0.00 %                

        **[tGravityAcc-mean()-X]**          numeric            180  0.00 %                

        **[tGravityAcc-mean()-Y]**          numeric            180  0.00 %                

        **[tGravityAcc-mean()-Z]**          numeric            180  0.00 %                

        **[tBodyAccJerk-mean()-X]**         numeric            180  0.00 %                

        **[tBodyAccJerk-mean()-Y]**         numeric            180  0.00 %                

        **[tBodyAccJerk-mean()-Z]**         numeric            180  0.00 %                

        **[tBodyGyro-mean()-X]**            numeric            180  0.00 %                

        **[tBodyGyro-mean()-Y]**            numeric            180  0.00 %                

        **[tBodyGyro-mean()-Z]**            numeric            180  0.00 %                

        **[tBodyGyroJerk-mean()-X]**        numeric            180  0.00 %                

        **[tBodyGyroJerk-mean()-Y]**        numeric            180  0.00 %                

        **[tBodyGyroJerk-mean()-Z]**        numeric            180  0.00 %                

        **[tBodyAccMag-mean()]**            numeric            180  0.00 %                

        **[tGravityAccMag-mean()]**         numeric            180  0.00 %                

        **[tBodyAccJerkMag-mean()]**        numeric            180  0.00 %                

        **[tBodyGyroMag-mean()]**           numeric            180  0.00 %                

        **[tBodyGyroJerkMag-mean()]**       numeric            180  0.00 %                

        **[fBodyAcc-mean()-X]**             numeric            180  0.00 %                

        **[fBodyAcc-mean()-Y]**             numeric            180  0.00 %                

        **[fBodyAcc-mean()-Z]**             numeric            180  0.00 %                

        **[fBodyAccJerk-mean()-X]**         numeric            180  0.00 %                

        **[fBodyAccJerk-mean()-Y]**         numeric            180  0.00 %                

        **[fBodyAccJerk-mean()-Z]**         numeric            180  0.00 %                

        **[fBodyGyro-mean()-X]**            numeric            180  0.00 %                

        **[fBodyGyro-mean()-Y]**            numeric            180  0.00 %                

        **[fBodyGyro-mean()-Z]**            numeric            180  0.00 %                

        **[fBodyAccMag-mean()]**            numeric            180  0.00 %                

        **[fBodyBodyAccJerkMag-mean()]**    numeric            180  0.00 %                

        **[fBodyBodyGyroMag-mean()]**       numeric            180  0.00 %                

        **[fBodyBodyGyroJerkMag-mean()]**   numeric            180  0.00 %                

        **[tBodyAcc-std()-X]**              numeric            180  0.00 %                

        **[tBodyAcc-std()-Y]**              numeric            180  0.00 %                

        **[tBodyAcc-std()-Z]**              numeric            180  0.00 %                

        **[tGravityAcc-std()-X]**           numeric            180  0.00 %                

        **[tGravityAcc-std()-Y]**           numeric            180  0.00 %                

        **[tGravityAcc-std()-Z]**           numeric            180  0.00 %                

        **[tBodyAccJerk-std()-X]**          numeric            180  0.00 %                

        **[tBodyAccJerk-std()-Y]**          numeric            180  0.00 %                

        **[tBodyAccJerk-std()-Z]**          numeric            180  0.00 %                

        **[tBodyGyro-std()-X]**             numeric            180  0.00 %                

        **[tBodyGyro-std()-Y]**             numeric            180  0.00 %                

        **[tBodyGyro-std()-Z]**             numeric            180  0.00 %                

        **[tBodyGyroJerk-std()-X]**         numeric            180  0.00 %                

        **[tBodyGyroJerk-std()-Y]**         numeric            180  0.00 %                

        **[tBodyGyroJerk-std()-Z]**         numeric            180  0.00 %                

        **[tBodyAccMag-std()]**             numeric            180  0.00 %                

        **[tGravityAccMag-std()]**          numeric            180  0.00 %                

        **[tBodyAccJerkMag-std()]**         numeric            180  0.00 %                

        **[tBodyGyroMag-std()]**            numeric            180  0.00 %                

        **[tBodyGyroJerkMag-std()]**        numeric            180  0.00 %                

        **[fBodyAcc-std()-X]**              numeric            180  0.00 %                

        **[fBodyAcc-std()-Y]**              numeric            180  0.00 %                

        **[fBodyAcc-std()-Z]**              numeric            180  0.00 %                

        **[fBodyAccJerk-std()-X]**          numeric            180  0.00 %                

        **[fBodyAccJerk-std()-Y]**          numeric            180  0.00 %                

        **[fBodyAccJerk-std()-Z]**          numeric            180  0.00 %                

        **[fBodyGyro-std()-X]**             numeric            180  0.00 %                

        **[fBodyGyro-std()-Y]**             numeric            180  0.00 %                

        **[fBodyGyro-std()-Z]**             numeric            180  0.00 %                

        **[fBodyAccMag-std()]**             numeric            180  0.00 %                

        **[fBodyBodyAccJerkMag-std()]**     numeric            180  0.00 %                

        **[fBodyBodyGyroMag-std()]**        numeric            180  0.00 %                

        **[fBodyBodyGyroJerkMag-std()]**    numeric            180  0.00 %                
------------------------------------------------------------------------------------------




# Variable list
## Subjects

<div class = "row">
<div class = "col-lg-8">

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               integer

Number of missing obs.      0 (0 %)

Number of unique values          30

Median                         15.5

1st and 3rd quartiles         8; 23

Min. and max.                 1; 30
-----------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-1-Subjects', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(0, 5, 10, 15, 20, 25
), xmax = c(5, 10, 15, 20, 25, 30), ymin = c(0, 0, 0, 0, 0, 0
), ymax = c(30L, 30L, 30L, 30L, 30L, 30L)), .Names = c("xmin", 
"xmax", "ymin", "ymax"), row.names = c(NA, -6L), class = "data.frame"), 
    vnam = "Subjects")
```
</div>
</div>




---

## Activity

<div class = "row">
<div class = "col-lg-8">

-------------------------------------
Feature                        Result
------------------------- -----------
Variable type               character

Number of missing obs.        0 (0 %)

Number of unique values             6

Mode                         "LAYING"
-------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-2-Activity', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:6, .Label = c("LAYING", 
"SITTING", "STANDING", "WALKING", "WALKING_DOWNSTAIRS", "WALKING_UPSTAIRS"
), class = "factor"), y = c(30L, 30L, 30L, 30L, 30L, 30L)), .Names = c("x", 
"y"), row.names = c(NA, -6L), class = "data.frame"), vnam = "Activity")
```
</div>
</div>


- Observed factor levels: \"LAYING\", \"SITTING\", \"STANDING\", \"WALKING\", \"WALKING_DOWNSTAIRS\", \"WALKING_UPSTAIRS\". 



---

## tBodyAcc-mean()-X

<div class = "row">
<div class = "col-lg-8">

--------------------------------------
Feature                         Result
------------------------- ------------
Variable type                  numeric

Number of missing obs.         0 (0 %)

Number of unique values            180

Median                            0.28

1st and 3rd quartiles       0.27; 0.28

Min. and max.                0.22; 0.3
--------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-3-tBodyAcc-mean()-X', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(0.22, 0.23, 0.24, 0.25, 
0.26, 0.27, 0.28, 0.29, 0.3), xmax = c(0.23, 0.24, 0.25, 0.26, 
0.27, 0.28, 0.29, 0.3, 0.31), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 
0), ymax = c(1L, 2L, 7L, 11L, 21L, 93L, 30L, 14L, 1L)), .Names = c("xmin", 
"xmax", "ymin", "ymax"), row.names = c(NA, -9L), class = "data.frame"), 
    vnam = "tBodyAcc-mean()-X")
```
</div>
</div>




---

## tBodyAcc-mean()-Y

<div class = "row">
<div class = "col-lg-8">

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Median                             -0.02

1st and 3rd quartiles       -0.02; -0.01

Min. and max.                   -0.04; 0
----------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-4-tBodyAcc-mean()-Y', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-0.045, -0.04, -0.035, 
-0.03, -0.025, -0.02, -0.015, -0.01, -0.005), xmax = c(-0.04, 
-0.035, -0.03, -0.025, -0.02, -0.015, -0.01, -0.005, 0), ymin = c(0, 
0, 0, 0, 0, 0, 0, 0, 0), ymax = c(1L, 0L, 6L, 15L, 25L, 87L, 
30L, 14L, 2L)), .Names = c("xmin", "xmax", "ymin", "ymax"), row.names = c(NA, 
-9L), class = "data.frame"), vnam = "tBodyAcc-mean()-Y")
```
</div>
</div>




---

## tBodyAcc-mean()-Z

<div class = "row">
<div class = "col-lg-8">

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Median                             -0.11

1st and 3rd quartiles        -0.11; -0.1

Min. and max.               -0.15; -0.08
----------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-5-tBodyAcc-mean()-Z', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-0.16, -0.15, -0.14, 
-0.13, -0.12, -0.11, -0.1, -0.09, -0.08), xmax = c(-0.15, -0.14, 
-0.13, -0.12, -0.11, -0.1, -0.09, -0.08, -0.07), ymin = c(0, 
0, 0, 0, 0, 0, 0, 0, 0), ymax = c(2L, 1L, 2L, 15L, 48L, 92L, 
16L, 3L, 1L)), .Names = c("xmin", "xmax", "ymin", "ymax"), row.names = c(NA, 
-9L), class = "data.frame"), vnam = "tBodyAcc-mean()-Z")
```
</div>
</div>




---

## tGravityAcc-mean()-X

<div class = "row">
<div class = "col-lg-8">

---------------------------------------
Feature                          Result
------------------------- -------------
Variable type                   numeric

Number of missing obs.          0 (0 %)

Number of unique values             180

Median                             0.92

1st and 3rd quartiles        0.84; 0.94

Min. and max.               -0.68; 0.97
---------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-6-tGravityAcc-mean()-X', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-0.8, -0.6, -0.4, -0.2, 
0, 0.2, 0.4, 0.6, 0.8), xmax = c(-0.6, -0.4, -0.2, 0, 0.2, 0.4, 
0.6, 0.8, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0), ymax = c(2L, 
13L, 9L, 6L, 0L, 0L, 1L, 6L, 143L)), .Names = c("xmin", "xmax", 
"ymin", "ymax"), row.names = c(NA, -9L), class = "data.frame"), 
    vnam = "tGravityAcc-mean()-X")
```
</div>
</div>




---

## tGravityAcc-mean()-Y

<div class = "row">
<div class = "col-lg-8">

---------------------------------------
Feature                          Result
------------------------- -------------
Variable type                   numeric

Number of missing obs.          0 (0 %)

Number of unique values             180

Median                            -0.13

1st and 3rd quartiles       -0.23; 0.09

Min. and max.               -0.48; 0.96
---------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-7-tGravityAcc-mean()-Y', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-0.6, -0.4, -0.2, 0, 
0.2, 0.4, 0.6, 0.8), xmax = c(-0.4, -0.2, 0, 0.2, 0.4, 0.6, 0.8, 
1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0), ymax = c(3L, 66L, 61L, 
14L, 11L, 5L, 10L, 10L)), .Names = c("xmin", "xmax", "ymin", 
"ymax"), row.names = c(NA, -8L), class = "data.frame"), vnam = "tGravityAcc-mean()-Y")
```
</div>
</div>




---

## tGravityAcc-mean()-Z

<div class = "row">
<div class = "col-lg-8">

---------------------------------------
Feature                          Result
------------------------- -------------
Variable type                   numeric

Number of missing obs.          0 (0 %)

Number of unique values             180

Median                             0.02

1st and 3rd quartiles       -0.12; 0.15

Min. and max.                -0.5; 0.96
---------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-8-tGravityAcc-mean()-Z', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-0.6, -0.4, -0.2, 0, 
0.2, 0.4, 0.6, 0.8), xmax = c(-0.4, -0.2, 0, 0.2, 0.4, 0.6, 0.8, 
1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0), ymax = c(3L, 18L, 60L, 
63L, 13L, 7L, 10L, 6L)), .Names = c("xmin", "xmax", "ymin", "ymax"
), row.names = c(NA, -8L), class = "data.frame"), vnam = "tGravityAcc-mean()-Z")
```
</div>
</div>




---

## tBodyAccJerk-mean()-X

<div class = "row">
<div class = "col-lg-8">

--------------------------------------
Feature                         Result
------------------------- ------------
Variable type                  numeric

Number of missing obs.         0 (0 %)

Number of unique values            180

Median                            0.08

1st and 3rd quartiles       0.07; 0.08

Min. and max.               0.04; 0.13
--------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-9-tBodyAccJerk-mean()-X', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(0.04, 0.05, 0.06, 0.07, 
0.08, 0.09, 0.1, 0.11, 0.12, 0.13), xmax = c(0.05, 0.06, 0.07, 
0.08, 0.09, 0.1, 0.11, 0.12, 0.13, 0.14), ymin = c(0, 0, 0, 0, 
0, 0, 0, 0, 0, 0), ymax = c(3L, 4L, 13L, 98L, 34L, 14L, 8L, 5L, 
0L, 1L)), .Names = c("xmin", "xmax", "ymin", "ymax"), row.names = c(NA, 
-10L), class = "data.frame"), vnam = "tBodyAccJerk-mean()-X")
```
</div>
</div>




---

## tBodyAccJerk-mean()-Y

<div class = "row">
<div class = "col-lg-8">

---------------------------------------
Feature                          Result
------------------------- -------------
Variable type                   numeric

Number of missing obs.          0 (0 %)

Number of unique values             180

Median                             0.01

1st and 3rd quartiles           0; 0.01

Min. and max.               -0.04; 0.06
---------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-10-tBodyAccJerk-mean()-Y', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-0.04, -0.03, -0.02, 
-0.01, 0, 0.01, 0.02, 0.03, 0.04, 0.05), xmax = c(-0.03, -0.02, 
-0.01, 0, 0.01, 0.02, 0.03, 0.04, 0.05, 0.06), ymin = c(0, 0, 
0, 0, 0, 0, 0, 0, 0, 0), ymax = c(2L, 3L, 13L, 26L, 52L, 59L, 
18L, 6L, 0L, 1L)), .Names = c("xmin", "xmax", "ymin", "ymax"), row.names = c(NA, 
-10L), class = "data.frame"), vnam = "tBodyAccJerk-mean()-Y")
```
</div>
</div>




---

## tBodyAccJerk-mean()-Z

<div class = "row">
<div class = "col-lg-8">

---------------------------------------
Feature                          Result
------------------------- -------------
Variable type                   numeric

Number of missing obs.          0 (0 %)

Number of unique values             180

Median                                0

1st and 3rd quartiles          -0.01; 0

Min. and max.               -0.07; 0.04
---------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-11-tBodyAccJerk-mean()-Z', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-0.07, -0.06, -0.05, 
-0.04, -0.03, -0.02, -0.01, 0, 0.01, 0.02, 0.03), xmax = c(-0.06, 
-0.05, -0.04, -0.03, -0.02, -0.01, 0, 0.01, 0.02, 0.03, 0.04), 
    ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0), ymax = c(1L, 1L, 
    1L, 6L, 12L, 27L, 77L, 41L, 9L, 3L, 2L)), .Names = c("xmin", 
"xmax", "ymin", "ymax"), row.names = c(NA, -11L), class = "data.frame"), 
    vnam = "tBodyAccJerk-mean()-Z")
```
</div>
</div>




---

## tBodyGyro-mean()-X

<div class = "row">
<div class = "col-lg-8">

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Median                             -0.03

1st and 3rd quartiles       -0.05; -0.02

Min. and max.                -0.21; 0.19
----------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-12-tBodyGyro-mean()-X', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-0.25, -0.2, -0.15, 
-0.1, -0.05, 0, 0.05, 0.1, 0.15), xmax = c(-0.2, -0.15, -0.1, 
-0.05, 0, 0.05, 0.1, 0.15, 0.2), ymin = c(0, 0, 0, 0, 0, 0, 0, 
0, 0), ymax = c(1L, 2L, 18L, 20L, 113L, 11L, 13L, 1L, 1L)), .Names = c("xmin", 
"xmax", "ymin", "ymax"), row.names = c(NA, -9L), class = "data.frame"), 
    vnam = "tBodyGyro-mean()-X")
```
</div>
</div>




---

## tBodyGyro-mean()-Y

<div class = "row">
<div class = "col-lg-8">

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Median                             -0.07

1st and 3rd quartiles       -0.09; -0.06

Min. and max.                 -0.2; 0.03
----------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-13-tBodyGyro-mean()-Y', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-0.22, -0.2, -0.18, 
-0.16, -0.14, -0.12, -0.1, -0.08, -0.06, -0.04, -0.02, 0, 0.02
), xmax = c(-0.2, -0.18, -0.16, -0.14, -0.12, -0.1, -0.08, -0.06, 
-0.04, -0.02, 0, 0.02, 0.04), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(1L, 1L, 2L, 5L, 5L, 12L, 38L, 72L, 23L, 
9L, 5L, 5L, 2L)), .Names = c("xmin", "xmax", "ymin", "ymax"), row.names = c(NA, 
-13L), class = "data.frame"), vnam = "tBodyGyro-mean()-Y")
```
</div>
</div>




---

## tBodyGyro-mean()-Z

<div class = "row">
<div class = "col-lg-8">

---------------------------------------
Feature                          Result
------------------------- -------------
Variable type                   numeric

Number of missing obs.          0 (0 %)

Number of unique values             180

Median                             0.09

1st and 3rd quartiles         0.07; 0.1

Min. and max.               -0.07; 0.18
---------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-14-tBodyGyro-mean()-Z', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-0.08, -0.06, -0.04, 
-0.02, 0, 0.02, 0.04, 0.06, 0.08, 0.1, 0.12, 0.14, 0.16), xmax = c(-0.06, 
-0.04, -0.02, 0, 0.02, 0.04, 0.06, 0.08, 0.1, 0.12, 0.14, 0.16, 
0.18), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0), ymax = c(1L, 
1L, 1L, 3L, 2L, 4L, 11L, 36L, 74L, 23L, 8L, 13L, 3L)), .Names = c("xmin", 
"xmax", "ymin", "ymax"), row.names = c(NA, -13L), class = "data.frame"), 
    vnam = "tBodyGyro-mean()-Z")
```
</div>
</div>




---

## tBodyGyroJerk-mean()-X

<div class = "row">
<div class = "col-lg-8">

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Median                              -0.1

1st and 3rd quartiles        -0.1; -0.09

Min. and max.               -0.16; -0.02
----------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-15-tBodyGyroJerk-mean()-X', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-0.16, -0.14, -0.12, 
-0.1, -0.08, -0.06, -0.04), xmax = c(-0.14, -0.12, -0.1, -0.08, 
-0.06, -0.04, -0.02), ymin = c(0, 0, 0, 0, 0, 0, 0), ymax = c(10L, 
10L, 55L, 76L, 16L, 7L, 6L)), .Names = c("xmin", "xmax", "ymin", 
"ymax"), row.names = c(NA, -7L), class = "data.frame"), vnam = "tBodyGyroJerk-mean()-X")
```
</div>
</div>




---

## tBodyGyroJerk-mean()-Y

<div class = "row">
<div class = "col-lg-8">

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Median                             -0.04

1st and 3rd quartiles       -0.05; -0.04

Min. and max.               -0.08; -0.01
----------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-16-tBodyGyroJerk-mean()-Y', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-0.08, -0.07, -0.06, 
-0.05, -0.04, -0.03, -0.02), xmax = c(-0.07, -0.06, -0.05, -0.04, 
-0.03, -0.02, -0.01), ymin = c(0, 0, 0, 0, 0, 0, 0), ymax = c(5L, 
5L, 21L, 78L, 62L, 6L, 3L)), .Names = c("xmin", "xmax", "ymin", 
"ymax"), row.names = c(NA, -7L), class = "data.frame"), vnam = "tBodyGyroJerk-mean()-Y")
```
</div>
</div>




---

## tBodyGyroJerk-mean()-Z

<div class = "row">
<div class = "col-lg-8">

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Median                             -0.05

1st and 3rd quartiles       -0.06; -0.05

Min. and max.               -0.09; -0.01
----------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-17-tBodyGyroJerk-mean()-Z', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-0.1, -0.09, -0.08, 
-0.07, -0.06, -0.05, -0.04, -0.03, -0.02, -0.01), xmax = c(-0.09, 
-0.08, -0.07, -0.06, -0.05, -0.04, -0.03, -0.02, -0.01, 0), ymin = c(0, 
0, 0, 0, 0, 0, 0, 0, 0, 0), ymax = c(2L, 1L, 17L, 33L, 74L, 36L, 
11L, 4L, 1L, 1L)), .Names = c("xmin", "xmax", "ymin", "ymax"), row.names = c(NA, 
-10L), class = "data.frame"), vnam = "tBodyGyroJerk-mean()-Z")
```
</div>
</div>




---

## tBodyAccMag-mean()

<div class = "row">
<div class = "col-lg-8">

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Median                             -0.48

1st and 3rd quartiles       -0.96; -0.09

Min. and max.                -0.99; 0.64
----------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-18-tBodyAccMag-mean()', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.8, -0.6, -0.4, 
-0.2, 0, 0.2, 0.4, 0.6), xmax = c(-0.8, -0.6, -0.4, -0.2, 0, 
0.2, 0.4, 0.6, 0.8), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0), ymax = c(89L, 
0L, 2L, 17L, 37L, 26L, 8L, 0L, 1L)), .Names = c("xmin", "xmax", 
"ymin", "ymax"), row.names = c(NA, -9L), class = "data.frame"), 
    vnam = "tBodyAccMag-mean()")
```
</div>
</div>




---

## tGravityAccMag-mean()

<div class = "row">
<div class = "col-lg-8">

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Median                             -0.48

1st and 3rd quartiles       -0.96; -0.09

Min. and max.                -0.99; 0.64
----------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-19-tGravityAccMag-mean()', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.8, -0.6, -0.4, 
-0.2, 0, 0.2, 0.4, 0.6), xmax = c(-0.8, -0.6, -0.4, -0.2, 0, 
0.2, 0.4, 0.6, 0.8), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0), ymax = c(89L, 
0L, 2L, 17L, 37L, 26L, 8L, 0L, 1L)), .Names = c("xmin", "xmax", 
"ymin", "ymax"), row.names = c(NA, -9L), class = "data.frame"), 
    vnam = "tGravityAccMag-mean()")
```
</div>
</div>




---

## tBodyAccJerkMag-mean()

<div class = "row">
<div class = "col-lg-8">

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Median                             -0.82

1st and 3rd quartiles       -0.98; -0.25

Min. and max.                -0.99; 0.43
----------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-20-tBodyAccJerkMag-mean()', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.8, -0.6, -0.4, 
-0.2, 0, 0.2, 0.4), xmax = c(-0.8, -0.6, -0.4, -0.2, 0, 0.2, 
0.4, 0.6), ymin = c(0, 0, 0, 0, 0, 0, 0, 0), ymax = c(90L, 2L, 
17L, 33L, 29L, 7L, 1L, 1L)), .Names = c("xmin", "xmax", "ymin", 
"ymax"), row.names = c(NA, -8L), class = "data.frame"), vnam = "tBodyAccJerkMag-mean()")
```
</div>
</div>




---

## tBodyGyroMag-mean()

<div class = "row">
<div class = "col-lg-8">

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Median                             -0.66

1st and 3rd quartiles       -0.95; -0.22

Min. and max.                -0.98; 0.42
----------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-21-tBodyGyroMag-mean()', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.8, -0.6, -0.4, 
-0.2, 0, 0.2, 0.4), xmax = c(-0.8, -0.6, -0.4, -0.2, 0, 0.2, 
0.4, 0.6), ymin = c(0, 0, 0, 0, 0, 0, 0, 0), ymax = c(90L, 0L, 
7L, 42L, 28L, 11L, 1L, 1L)), .Names = c("xmin", "xmax", "ymin", 
"ymax"), row.names = c(NA, -8L), class = "data.frame"), vnam = "tBodyGyroMag-mean()")
```
</div>
</div>




---

## tBodyGyroJerkMag-mean()

<div class = "row">
<div class = "col-lg-8">

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Median                             -0.86

1st and 3rd quartiles       -0.99; -0.51

Min. and max.                   -1; 0.09
----------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-22-tBodyGyroJerkMag-mean()', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0), xmax = c(-0.9, -0.8, 
-0.7, -0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1), ymin = c(0, 
0, 0, 0, 0, 0, 0, 0, 0, 0, 0), ymax = c(90L, 0L, 6L, 19L, 26L, 
16L, 12L, 4L, 3L, 2L, 2L)), .Names = c("xmin", "xmax", "ymin", 
"ymax"), row.names = c(NA, -11L), class = "data.frame"), vnam = "tBodyGyroJerkMag-mean()")
```
</div>
</div>




---

## fBodyAcc-mean()-X

<div class = "row">
<div class = "col-lg-8">

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Median                             -0.77

1st and 3rd quartiles       -0.98; -0.22

Min. and max.                   -1; 0.54
----------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-23-fBodyAcc-mean()-X', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.8, -0.6, -0.4, 
-0.2, 0, 0.2, 0.4), xmax = c(-0.8, -0.6, -0.4, -0.2, 0, 0.2, 
0.4, 0.6), ymin = c(0, 0, 0, 0, 0, 0, 0, 0), ymax = c(90L, 1L, 
9L, 36L, 23L, 16L, 4L, 1L)), .Names = c("xmin", "xmax", "ymin", 
"ymax"), row.names = c(NA, -8L), class = "data.frame"), vnam = "fBodyAcc-mean()-X")
```
</div>
</div>




---

## fBodyAcc-mean()-Y

<div class = "row">
<div class = "col-lg-8">

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Median                             -0.59

1st and 3rd quartiles       -0.95; -0.06

Min. and max.                -0.99; 0.52
----------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-24-fBodyAcc-mean()-Y', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.8, -0.6, -0.4, 
-0.2, 0, 0.2, 0.4), xmax = c(-0.8, -0.6, -0.4, -0.2, 0, 0.2, 
0.4, 0.6), ymin = c(0, 0, 0, 0, 0, 0, 0, 0), ymax = c(89L, 1L, 
1L, 14L, 40L, 25L, 7L, 3L)), .Names = c("xmin", "xmax", "ymin", 
"ymax"), row.names = c(NA, -8L), class = "data.frame"), vnam = "fBodyAcc-mean()-Y")
```
</div>
</div>




---

## fBodyAcc-mean()-Z

<div class = "row">
<div class = "col-lg-8">

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Median                             -0.72

1st and 3rd quartiles       -0.96; -0.32

Min. and max.                -0.99; 0.28
----------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-25-fBodyAcc-mean()-Z', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.8, -0.6, -0.4, 
-0.2, 0, 0.2), xmax = c(-0.8, -0.6, -0.4, -0.2, 0, 0.2, 0.4), 
    ymin = c(0, 0, 0, 0, 0, 0, 0), ymax = c(90L, 2L, 28L, 40L, 
    13L, 5L, 2L)), .Names = c("xmin", "xmax", "ymin", "ymax"), row.names = c(NA, 
-7L), class = "data.frame"), vnam = "fBodyAcc-mean()-Z")
```
</div>
</div>




---

## fBodyAccJerk-mean()-X

<div class = "row">
<div class = "col-lg-8">

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Median                             -0.81

1st and 3rd quartiles       -0.98; -0.28

Min. and max.                -0.99; 0.47
----------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-26-fBodyAccJerk-mean()-X', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.8, -0.6, -0.4, 
-0.2, 0, 0.2, 0.4), xmax = c(-0.8, -0.6, -0.4, -0.2, 0, 0.2, 
0.4, 0.6), ymin = c(0, 0, 0, 0, 0, 0, 0, 0), ymax = c(90L, 2L, 
21L, 35L, 23L, 6L, 2L, 1L)), .Names = c("xmin", "xmax", "ymin", 
"ymax"), row.names = c(NA, -8L), class = "data.frame"), vnam = "fBodyAccJerk-mean()-X")
```
</div>
</div>




---

## fBodyAccJerk-mean()-Y

<div class = "row">
<div class = "col-lg-8">

---------------------------------------
Feature                          Result
------------------------- -------------
Variable type                   numeric

Number of missing obs.          0 (0 %)

Number of unique values             180

Median                            -0.78

1st and 3rd quartiles       -0.97; -0.2

Min. and max.               -0.99; 0.28
---------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-27-fBodyAccJerk-mean()-Y', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.8, -0.6, -0.4, 
-0.2, 0, 0.2), xmax = c(-0.8, -0.6, -0.4, -0.2, 0, 0.2, 0.4), 
    ymin = c(0, 0, 0, 0, 0, 0, 0), ymax = c(90L, 2L, 14L, 28L, 
    34L, 9L, 3L)), .Names = c("xmin", "xmax", "ymin", "ymax"), row.names = c(NA, 
-7L), class = "data.frame"), vnam = "fBodyAccJerk-mean()-Y")
```
</div>
</div>




---

## fBodyAccJerk-mean()-Z

<div class = "row">
<div class = "col-lg-8">

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Median                             -0.87

1st and 3rd quartiles       -0.98; -0.47

Min. and max.                -0.99; 0.16
----------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-28-fBodyAccJerk-mean()-Z', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.0999999999999999), xmax = c(-0.9, 
-0.8, -0.7, -0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.0999999999999999, 
0.2), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0), ymax = c(90L, 
0L, 6L, 17L, 15L, 17L, 16L, 11L, 3L, 2L, 2L, 1L)), .Names = c("xmin", 
"xmax", "ymin", "ymax"), row.names = c(NA, -12L), class = "data.frame"), 
    vnam = "fBodyAccJerk-mean()-Z")
```
</div>
</div>




---

## fBodyGyro-mean()-X

<div class = "row">
<div class = "col-lg-8">

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Median                             -0.73

1st and 3rd quartiles       -0.97; -0.34

Min. and max.                -0.99; 0.47
----------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-29-fBodyGyro-mean()-X', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.8, -0.6, -0.4, 
-0.2, 0, 0.2, 0.4), xmax = c(-0.8, -0.6, -0.4, -0.2, 0, 0.2, 
0.4, 0.6), ymin = c(0, 0, 0, 0, 0, 0, 0, 0), ymax = c(90L, 1L, 
29L, 41L, 16L, 1L, 1L, 1L)), .Names = c("xmin", "xmax", "ymin", 
"ymax"), row.names = c(NA, -8L), class = "data.frame"), vnam = "fBodyGyro-mean()-X")
```
</div>
</div>




---

## fBodyGyro-mean()-Y

<div class = "row">
<div class = "col-lg-8">

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Median                             -0.81

1st and 3rd quartiles       -0.97; -0.45

Min. and max.                -0.99; 0.33
----------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-30-fBodyGyro-mean()-Y', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.8, -0.6, -0.4, 
-0.2, 0, 0.2), xmax = c(-0.8, -0.6, -0.4, -0.2, 0, 0.2, 0.4), 
    ymin = c(0, 0, 0, 0, 0, 0, 0), ymax = c(90L, 13L, 38L, 22L, 
    10L, 6L, 1L)), .Names = c("xmin", "xmax", "ymin", "ymax"), row.names = c(NA, 
-7L), class = "data.frame"), vnam = "fBodyGyro-mean()-Y")
```
</div>
</div>




---

## fBodyGyro-mean()-Z

<div class = "row">
<div class = "col-lg-8">

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Median                             -0.79

1st and 3rd quartiles       -0.96; -0.26

Min. and max.                -0.99; 0.49
----------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-31-fBodyGyro-mean()-Z', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.8, -0.6, -0.4, 
-0.2, 0, 0.2, 0.4), xmax = c(-0.8, -0.6, -0.4, -0.2, 0, 0.2, 
0.4, 0.6), ymin = c(0, 0, 0, 0, 0, 0, 0, 0), ymax = c(90L, 2L, 
17L, 41L, 21L, 6L, 2L, 1L)), .Names = c("xmin", "xmax", "ymin", 
"ymax"), row.names = c(NA, -8L), class = "data.frame"), vnam = "fBodyGyro-mean()-Z")
```
</div>
</div>




---

## fBodyAccMag-mean()

<div class = "row">
<div class = "col-lg-8">

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Median                             -0.67

1st and 3rd quartiles       -0.96; -0.16

Min. and max.                -0.99; 0.59
----------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-32-fBodyAccMag-mean()', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.8, -0.6, -0.4, 
-0.2, 0, 0.2, 0.4), xmax = c(-0.8, -0.6, -0.4, -0.2, 0, 0.2, 
0.4, 0.6), ymin = c(0, 0, 0, 0, 0, 0, 0, 0), ymax = c(89L, 1L, 
10L, 31L, 22L, 16L, 9L, 2L)), .Names = c("xmin", "xmax", "ymin", 
"ymax"), row.names = c(NA, -8L), class = "data.frame"), vnam = "fBodyAccMag-mean()")
```
</div>
</div>




---

## fBodyBodyAccJerkMag-mean()

<div class = "row">
<div class = "col-lg-8">

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Median                             -0.79

1st and 3rd quartiles       -0.98; -0.19

Min. and max.                -0.99; 0.54
----------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-33-fBodyBodyAccJerkMag-mean()', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.8, -0.6, -0.4, 
-0.2, 0, 0.2, 0.4), xmax = c(-0.8, -0.6, -0.4, -0.2, 0, 0.2, 
0.4, 0.6), ymin = c(0, 0, 0, 0, 0, 0, 0, 0), ymax = c(90L, 1L, 
16L, 25L, 26L, 17L, 4L, 1L)), .Names = c("xmin", "xmax", "ymin", 
"ymax"), row.names = c(NA, -8L), class = "data.frame"), vnam = "fBodyBodyAccJerkMag-mean()")
```
</div>
</div>




---

## fBodyBodyGyroMag-mean()

<div class = "row">
<div class = "col-lg-8">

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Median                             -0.77

1st and 3rd quartiles       -0.96; -0.41

Min. and max.                 -0.99; 0.2
----------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-34-fBodyBodyGyroMag-mean()', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2), xmax = c(-0.9, 
-0.8, -0.7, -0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 
0.3), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0), ymax = c(88L, 
2L, 0L, 8L, 20L, 18L, 22L, 9L, 4L, 5L, 1L, 2L, 1L)), .Names = c("xmin", 
"xmax", "ymin", "ymax"), row.names = c(NA, -13L), class = "data.frame"), 
    vnam = "fBodyBodyGyroMag-mean()")
```
</div>
</div>




---

## fBodyBodyGyroJerkMag-mean()

<div class = "row">
<div class = "col-lg-8">

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Median                             -0.88

1st and 3rd quartiles       -0.98; -0.58

Min. and max.                   -1; 0.15
----------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-35-fBodyBodyGyroJerkMag-mean()', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.0999999999999999), xmax = c(-0.9, 
-0.8, -0.7, -0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.0999999999999999, 
0.2), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0), ymax = c(90L, 
2L, 15L, 22L, 18L, 15L, 6L, 5L, 4L, 1L, 1L, 1L)), .Names = c("xmin", 
"xmax", "ymin", "ymax"), row.names = c(NA, -12L), class = "data.frame"), 
    vnam = "fBodyBodyGyroJerkMag-mean()")
```
</div>
</div>




---

## tBodyAcc-std()-X

<div class = "row">
<div class = "col-lg-8">

---------------------------------------
Feature                          Result
------------------------- -------------
Variable type                   numeric

Number of missing obs.          0 (0 %)

Number of unique values             180

Median                            -0.75

1st and 3rd quartiles       -0.98; -0.2

Min. and max.                  -1; 0.63
---------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-36-tBodyAcc-std()-X', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.8, -0.6, -0.4, 
-0.2, 0, 0.2, 0.4, 0.6), xmax = c(-0.8, -0.6, -0.4, -0.2, 0, 
0.2, 0.4, 0.6, 0.8), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0), ymax = c(90L, 
0L, 8L, 37L, 20L, 16L, 7L, 1L, 1L)), .Names = c("xmin", "xmax", 
"ymin", "ymax"), row.names = c(NA, -9L), class = "data.frame"), 
    vnam = "tBodyAcc-std()-X")
```
</div>
</div>




---

## tBodyAcc-std()-Y

<div class = "row">
<div class = "col-lg-8">

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Median                             -0.51

1st and 3rd quartiles       -0.94; -0.03

Min. and max.                -0.99; 0.62
----------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-37-tBodyAcc-std()-Y', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.8, -0.6, -0.4, 
-0.2, 0, 0.2, 0.4, 0.6), xmax = c(-0.8, -0.6, -0.4, -0.2, 0, 
0.2, 0.4, 0.6, 0.8), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0), ymax = c(89L, 
1L, 0L, 10L, 43L, 24L, 10L, 2L, 1L)), .Names = c("xmin", "xmax", 
"ymin", "ymax"), row.names = c(NA, -9L), class = "data.frame"), 
    vnam = "tBodyAcc-std()-Y")
```
</div>
</div>




---

## tBodyAcc-std()-Z

<div class = "row">
<div class = "col-lg-8">

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Median                             -0.65

1st and 3rd quartiles       -0.95; -0.23

Min. and max.                -0.99; 0.61
----------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-38-tBodyAcc-std()-Z', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.8, -0.6, -0.4, 
-0.2, 0, 0.2, 0.4, 0.6), xmax = c(-0.8, -0.6, -0.4, -0.2, 0, 
0.2, 0.4, 0.6, 0.8), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0), ymax = c(89L, 
1L, 15L, 42L, 20L, 10L, 1L, 1L, 1L)), .Names = c("xmin", "xmax", 
"ymin", "ymax"), row.names = c(NA, -9L), class = "data.frame"), 
    vnam = "tBodyAcc-std()-Z")
```
</div>
</div>




---

## tGravityAcc-std()-X

<div class = "row">
<div class = "col-lg-8">

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Median                             -0.97

1st and 3rd quartiles       -0.98; -0.95

Min. and max.                  -1; -0.83
----------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-39-tGravityAcc-std()-X', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.98, -0.96, -0.94, 
-0.92, -0.9, -0.88, -0.86, -0.84), xmax = c(-0.98, -0.96, -0.94, 
-0.92, -0.9, -0.88, -0.86, -0.84, -0.82), ymin = c(0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(55L, 52L, 52L, 12L, 4L, 3L, 1L, 0L, 
1L)), .Names = c("xmin", "xmax", "ymin", "ymax"), row.names = c(NA, 
-9L), class = "data.frame"), vnam = "tGravityAcc-std()-X")
```
</div>
</div>




---

## tGravityAcc-std()-Y

<div class = "row">
<div class = "col-lg-8">

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Median                             -0.96

1st and 3rd quartiles       -0.97; -0.94

Min. and max.               -0.99; -0.64
----------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-40-tGravityAcc-std()-Y', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.95, -0.9, -0.85, 
-0.8, -0.75, -0.7, -0.65), xmax = c(-0.95, -0.9, -0.85, -0.8, 
-0.75, -0.7, -0.65, -0.6), ymin = c(0, 0, 0, 0, 0, 0, 0, 0), 
    ymax = c(107L, 72L, 0L, 0L, 0L, 0L, 0L, 1L)), .Names = c("xmin", 
"xmax", "ymin", "ymax"), row.names = c(NA, -8L), class = "data.frame"), 
    vnam = "tGravityAcc-std()-Y")
```
</div>
</div>




---

## tGravityAcc-std()-Z

<div class = "row">
<div class = "col-lg-8">

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Median                             -0.95

1st and 3rd quartiles       -0.96; -0.92

Min. and max.               -0.99; -0.61
----------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-41-tGravityAcc-std()-Z', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.95, -0.9, -0.85, 
-0.8, -0.75, -0.7, -0.65), xmax = c(-0.95, -0.9, -0.85, -0.8, 
-0.75, -0.7, -0.65, -0.6), ymin = c(0, 0, 0, 0, 0, 0, 0, 0), 
    ymax = c(79L, 76L, 23L, 1L, 0L, 0L, 0L, 1L)), .Names = c("xmin", 
"xmax", "ymin", "ymax"), row.names = c(NA, -8L), class = "data.frame"), 
    vnam = "tGravityAcc-std()-Z")
```
</div>
</div>




---

## tBodyAccJerk-std()-X

<div class = "row">
<div class = "col-lg-8">

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Median                             -0.81

1st and 3rd quartiles       -0.98; -0.22

Min. and max.                -0.99; 0.54
----------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-42-tBodyAccJerk-std()-X', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.8, -0.6, -0.4, 
-0.2, 0, 0.2, 0.4), xmax = c(-0.8, -0.6, -0.4, -0.2, 0, 0.2, 
0.4, 0.6), ymin = c(0, 0, 0, 0, 0, 0, 0, 0), ymax = c(90L, 2L, 
15L, 31L, 26L, 13L, 2L, 1L)), .Names = c("xmin", "xmax", "ymin", 
"ymax"), row.names = c(NA, -8L), class = "data.frame"), vnam = "tBodyAccJerk-std()-X")
```
</div>
</div>




---

## tBodyAccJerk-std()-Y

<div class = "row">
<div class = "col-lg-8">

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Median                             -0.78

1st and 3rd quartiles       -0.97; -0.15

Min. and max.                -0.99; 0.36
----------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-43-tBodyAccJerk-std()-Y', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.8, -0.6, -0.4, 
-0.2, 0, 0.2), xmax = c(-0.8, -0.6, -0.4, -0.2, 0, 0.2, 0.4), 
    ymin = c(0, 0, 0, 0, 0, 0, 0), ymax = c(90L, 1L, 10L, 28L, 
    32L, 12L, 7L)), .Names = c("xmin", "xmax", "ymin", "ymax"
), row.names = c(NA, -7L), class = "data.frame"), vnam = "tBodyAccJerk-std()-Y")
```
</div>
</div>




---

## tBodyAccJerk-std()-Z

<div class = "row">
<div class = "col-lg-8">

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Median                             -0.88

1st and 3rd quartiles       -0.98; -0.51

Min. and max.                -0.99; 0.03
----------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-44-tBodyAccJerk-std()-Z', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0), xmax = c(-0.9, -0.8, 
-0.7, -0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1), ymin = c(0, 
0, 0, 0, 0, 0, 0, 0, 0, 0, 0), ymax = c(90L, 1L, 11L, 16L, 19L, 
18L, 16L, 2L, 3L, 3L, 1L)), .Names = c("xmin", "xmax", "ymin", 
"ymax"), row.names = c(NA, -11L), class = "data.frame"), vnam = "tBodyAccJerk-std()-Z")
```
</div>
</div>




---

## tBodyGyro-std()-X

<div class = "row">
<div class = "col-lg-8">

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Median                             -0.79

1st and 3rd quartiles       -0.97; -0.44

Min. and max.                -0.99; 0.27
----------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-45-tBodyGyro-std()-X', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.8, -0.6, -0.4, 
-0.2, 0, 0.2), xmax = c(-0.8, -0.6, -0.4, -0.2, 0, 0.2, 0.4), 
    ymin = c(0, 0, 0, 0, 0, 0, 0), ymax = c(90L, 4L, 51L, 31L, 
    3L, 0L, 1L)), .Names = c("xmin", "xmax", "ymin", "ymax"), row.names = c(NA, 
-7L), class = "data.frame"), vnam = "tBodyGyro-std()-X")
```
</div>
</div>




---

## tBodyGyro-std()-Y

<div class = "row">
<div class = "col-lg-8">

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Median                              -0.8

1st and 3rd quartiles       -0.96; -0.42

Min. and max.                -0.99; 0.48
----------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-46-tBodyGyro-std()-Y', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.8, -0.6, -0.4, 
-0.2, 0, 0.2, 0.4), xmax = c(-0.8, -0.6, -0.4, -0.2, 0, 0.2, 
0.4, 0.6), ymin = c(0, 0, 0, 0, 0, 0, 0, 0), ymax = c(90L, 6L, 
43L, 18L, 12L, 8L, 2L, 1L)), .Names = c("xmin", "xmax", "ymin", 
"ymax"), row.names = c(NA, -8L), class = "data.frame"), vnam = "tBodyGyro-std()-Y")
```
</div>
</div>




---

## tBodyGyro-std()-Z

<div class = "row">
<div class = "col-lg-8">

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Median                              -0.8

1st and 3rd quartiles       -0.96; -0.31

Min. and max.                -0.99; 0.56
----------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-47-tBodyGyro-std()-Z', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.8, -0.6, -0.4, 
-0.2, 0, 0.2, 0.4), xmax = c(-0.8, -0.6, -0.4, -0.2, 0, 0.2, 
0.4, 0.6), ymin = c(0, 0, 0, 0, 0, 0, 0, 0), ymax = c(90L, 2L, 
20L, 42L, 20L, 3L, 2L, 1L)), .Names = c("xmin", "xmax", "ymin", 
"ymax"), row.names = c(NA, -8L), class = "data.frame"), vnam = "tBodyGyro-std()-Z")
```
</div>
</div>




---

## tBodyGyroJerk-std()-X

<div class = "row">
<div class = "col-lg-8">

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Median                             -0.84

1st and 3rd quartiles       -0.98; -0.46

Min. and max.                   -1; 0.18
----------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-48-tBodyGyroJerk-std()-X', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.0999999999999999), xmax = c(-0.9, 
-0.8, -0.7, -0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.0999999999999999, 
0.2), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0), ymax = c(90L, 
0L, 3L, 13L, 20L, 18L, 14L, 15L, 4L, 0L, 2L, 1L)), .Names = c("xmin", 
"xmax", "ymin", "ymax"), row.names = c(NA, -12L), class = "data.frame"), 
    vnam = "tBodyGyroJerk-std()-X")
```
</div>
</div>




---

## tBodyGyroJerk-std()-Y

<div class = "row">
<div class = "col-lg-8">

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Median                             -0.89

1st and 3rd quartiles       -0.98; -0.59

Min. and max.                    -1; 0.3
----------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-49-tBodyGyroJerk-std()-Y', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.8, -0.6, -0.4, 
-0.2, 0, 0.2), xmax = c(-0.8, -0.6, -0.4, -0.2, 0, 0.2, 0.4), 
    ymin = c(0, 0, 0, 0, 0, 0, 0), ymax = c(97L, 36L, 30L, 10L, 
    5L, 1L, 1L)), .Names = c("xmin", "xmax", "ymin", "ymax"), row.names = c(NA, 
-7L), class = "data.frame"), vnam = "tBodyGyroJerk-std()-Y")
```
</div>
</div>




---

## tBodyGyroJerk-std()-Z

<div class = "row">
<div class = "col-lg-8">

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Median                             -0.86

1st and 3rd quartiles       -0.98; -0.47

Min. and max.                   -1; 0.19
----------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-50-tBodyGyroJerk-std()-Z', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.0999999999999999), xmax = c(-0.9, 
-0.8, -0.7, -0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.0999999999999999, 
0.2), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0), ymax = c(90L, 
0L, 4L, 14L, 18L, 20L, 17L, 8L, 4L, 1L, 2L, 2L)), .Names = c("xmin", 
"xmax", "ymin", "ymax"), row.names = c(NA, -12L), class = "data.frame"), 
    vnam = "tBodyGyroJerk-std()-Z")
```
</div>
</div>




---

## tBodyAccMag-std()

<div class = "row">
<div class = "col-lg-8">

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Median                             -0.61

1st and 3rd quartiles       -0.94; -0.21

Min. and max.                -0.99; 0.43
----------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-51-tBodyAccMag-std()', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.8, -0.6, -0.4, 
-0.2, 0, 0.2, 0.4), xmax = c(-0.8, -0.6, -0.4, -0.2, 0, 0.2, 
0.4, 0.6), ymin = c(0, 0, 0, 0, 0, 0, 0, 0), ymax = c(88L, 2L, 
12L, 34L, 21L, 13L, 8L, 2L)), .Names = c("xmin", "xmax", "ymin", 
"ymax"), row.names = c(NA, -8L), class = "data.frame"), vnam = "tBodyAccMag-std()")
```
</div>
</div>




---

## tGravityAccMag-std()

<div class = "row">
<div class = "col-lg-8">

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Median                             -0.61

1st and 3rd quartiles       -0.94; -0.21

Min. and max.                -0.99; 0.43
----------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-52-tGravityAccMag-std()', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.8, -0.6, -0.4, 
-0.2, 0, 0.2, 0.4), xmax = c(-0.8, -0.6, -0.4, -0.2, 0, 0.2, 
0.4, 0.6), ymin = c(0, 0, 0, 0, 0, 0, 0, 0), ymax = c(88L, 2L, 
12L, 34L, 21L, 13L, 8L, 2L)), .Names = c("xmin", "xmax", "ymin", 
"ymax"), row.names = c(NA, -8L), class = "data.frame"), vnam = "tGravityAccMag-std()")
```
</div>
</div>




---

## tBodyAccJerkMag-std()

<div class = "row">
<div class = "col-lg-8">

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Median                              -0.8

1st and 3rd quartiles       -0.98; -0.22

Min. and max.                -0.99; 0.45
----------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-53-tBodyAccJerkMag-std()', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.8, -0.6, -0.4, 
-0.2, 0, 0.2, 0.4), xmax = c(-0.8, -0.6, -0.4, -0.2, 0, 0.2, 
0.4, 0.6), ymin = c(0, 0, 0, 0, 0, 0, 0, 0), ymax = c(90L, 1L, 
20L, 26L, 26L, 12L, 4L, 1L)), .Names = c("xmin", "xmax", "ymin", 
"ymax"), row.names = c(NA, -8L), class = "data.frame"), vnam = "tBodyAccJerkMag-std()")
```
</div>
</div>




---

## tBodyGyroMag-std()

<div class = "row">
<div class = "col-lg-8">

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Median                             -0.74

1st and 3rd quartiles       -0.95; -0.36

Min. and max.                 -0.98; 0.3
----------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-54-tBodyGyroMag-std()', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.8, -0.6, -0.4, 
-0.2, 0, 0.2), xmax = c(-0.8, -0.6, -0.4, -0.2, 0, 0.2, 0.4), 
    ymin = c(0, 0, 0, 0, 0, 0, 0), ymax = c(90L, 2L, 32L, 38L, 
    14L, 2L, 2L)), .Names = c("xmin", "xmax", "ymin", "ymax"), row.names = c(NA, 
-7L), class = "data.frame"), vnam = "tBodyGyroMag-std()")
```
</div>
</div>




---

## tBodyGyroJerkMag-std()

<div class = "row">
<div class = "col-lg-8">

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Median                             -0.88

1st and 3rd quartiles       -0.98; -0.58

Min. and max.                   -1; 0.25
----------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-55-tBodyGyroJerkMag-std()', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2), xmax = c(-0.9, 
-0.8, -0.7, -0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 
0.3), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0), ymax = c(90L, 
3L, 15L, 20L, 21L, 14L, 5L, 5L, 3L, 2L, 1L, 0L, 1L)), .Names = c("xmin", 
"xmax", "ymin", "ymax"), row.names = c(NA, -13L), class = "data.frame"), 
    vnam = "tBodyGyroJerkMag-std()")
```
</div>
</div>




---

## fBodyAcc-std()-X

<div class = "row">
<div class = "col-lg-8">

---------------------------------------
Feature                          Result
------------------------- -------------
Variable type                   numeric

Number of missing obs.          0 (0 %)

Number of unique values             180

Median                            -0.75

1st and 3rd quartiles       -0.98; -0.2

Min. and max.                  -1; 0.66
---------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-56-fBodyAcc-std()-X', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.8, -0.6, -0.4, 
-0.2, 0, 0.2, 0.4, 0.6), xmax = c(-0.8, -0.6, -0.4, -0.2, 0, 
0.2, 0.4, 0.6, 0.8), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0), ymax = c(90L, 
0L, 7L, 37L, 22L, 13L, 7L, 3L, 1L)), .Names = c("xmin", "xmax", 
"ymin", "ymax"), row.names = c(NA, -9L), class = "data.frame"), 
    vnam = "fBodyAcc-std()-X")
```
</div>
</div>




---

## fBodyAcc-std()-Y

<div class = "row">
<div class = "col-lg-8">

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Median                             -0.51

1st and 3rd quartiles       -0.94; -0.08

Min. and max.                -0.99; 0.56
----------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-57-fBodyAcc-std()-Y', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.8, -0.6, -0.4, 
-0.2, 0, 0.2, 0.4), xmax = c(-0.8, -0.6, -0.4, -0.2, 0, 0.2, 
0.4, 0.6), ymin = c(0, 0, 0, 0, 0, 0, 0, 0), ymax = c(89L, 1L, 
0L, 14L, 41L, 24L, 8L, 3L)), .Names = c("xmin", "xmax", "ymin", 
"ymax"), row.names = c(NA, -8L), class = "data.frame"), vnam = "fBodyAcc-std()-Y")
```
</div>
</div>




---

## fBodyAcc-std()-Z

<div class = "row">
<div class = "col-lg-8">

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Median                             -0.64

1st and 3rd quartiles       -0.95; -0.27

Min. and max.                -0.99; 0.69
----------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-58-fBodyAcc-std()-Z', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.8, -0.6, -0.4, 
-0.2, 0, 0.2, 0.4, 0.6), xmax = c(-0.8, -0.6, -0.4, -0.2, 0, 
0.2, 0.4, 0.6, 0.8), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0), ymax = c(89L, 
1L, 19L, 40L, 19L, 9L, 1L, 1L, 1L)), .Names = c("xmin", "xmax", 
"ymin", "ymax"), row.names = c(NA, -9L), class = "data.frame"), 
    vnam = "fBodyAcc-std()-Z")
```
</div>
</div>




---

## fBodyAccJerk-std()-X

<div class = "row">
<div class = "col-lg-8">

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Median                             -0.83

1st and 3rd quartiles       -0.98; -0.25

Min. and max.                   -1; 0.48
----------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-59-fBodyAccJerk-std()-X', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.8, -0.6, -0.4, 
-0.2, 0, 0.2, 0.4), xmax = c(-0.8, -0.6, -0.4, -0.2, 0, 0.2, 
0.4, 0.6), ymin = c(0, 0, 0, 0, 0, 0, 0, 0), ymax = c(90L, 2L, 
21L, 30L, 25L, 11L, 0L, 1L)), .Names = c("xmin", "xmax", "ymin", 
"ymax"), row.names = c(NA, -8L), class = "data.frame"), vnam = "fBodyAccJerk-std()-X")
```
</div>
</div>




---

## fBodyAccJerk-std()-Y

<div class = "row">
<div class = "col-lg-8">

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Median                             -0.79

1st and 3rd quartiles       -0.97; -0.17

Min. and max.                -0.99; 0.35
----------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-60-fBodyAccJerk-std()-Y', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.8, -0.6, -0.4, 
-0.2, 0, 0.2), xmax = c(-0.8, -0.6, -0.4, -0.2, 0, 0.2, 0.4), 
    ymin = c(0, 0, 0, 0, 0, 0, 0), ymax = c(90L, 2L, 11L, 28L, 
    33L, 9L, 7L)), .Names = c("xmin", "xmax", "ymin", "ymax"), row.names = c(NA, 
-7L), class = "data.frame"), vnam = "fBodyAccJerk-std()-Y")
```
</div>
</div>




---

## fBodyAccJerk-std()-Z

<div class = "row">
<div class = "col-lg-8">

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Median                              -0.9

1st and 3rd quartiles       -0.98; -0.54

Min. and max.               -0.99; -0.01
----------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-61-fBodyAccJerk-std()-Z', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1), xmax = c(-0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0), ymin = c(0, 0, 0, 0, 
0, 0, 0, 0, 0, 0), ymax = c(90L, 2L, 13L, 20L, 22L, 15L, 10L, 
3L, 1L, 4L)), .Names = c("xmin", "xmax", "ymin", "ymax"), row.names = c(NA, 
-10L), class = "data.frame"), vnam = "fBodyAccJerk-std()-Z")
```
</div>
</div>




---

## fBodyGyro-std()-X

<div class = "row">
<div class = "col-lg-8">

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Median                             -0.81

1st and 3rd quartiles       -0.98; -0.48

Min. and max.                 -0.99; 0.2
----------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-62-fBodyGyro-std()-X', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.0999999999999999), xmax = c(-0.9, 
-0.8, -0.7, -0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.0999999999999999, 
0.2), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0), ymax = c(85L, 
5L, 1L, 10L, 28L, 21L, 22L, 6L, 1L, 0L, 0L, 1L)), .Names = c("xmin", 
"xmax", "ymin", "ymax"), row.names = c(NA, -12L), class = "data.frame"), 
    vnam = "fBodyGyro-std()-X")
```
</div>
</div>




---

## fBodyGyro-std()-Y

<div class = "row">
<div class = "col-lg-8">

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Median                              -0.8

1st and 3rd quartiles       -0.96; -0.42

Min. and max.                -0.99; 0.65
----------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-63-fBodyGyro-std()-Y', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.8, -0.6, -0.4, 
-0.2, 0, 0.2, 0.4, 0.6), xmax = c(-0.8, -0.6, -0.4, -0.2, 0, 
0.2, 0.4, 0.6, 0.8), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0), ymax = c(90L, 
4L, 42L, 21L, 12L, 8L, 2L, 0L, 1L)), .Names = c("xmin", "xmax", 
"ymin", "ymax"), row.names = c(NA, -9L), class = "data.frame"), 
    vnam = "fBodyGyro-std()-Y")
```
</div>
</div>




---

## fBodyGyro-std()-Z

<div class = "row">
<div class = "col-lg-8">

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Median                             -0.82

1st and 3rd quartiles       -0.96; -0.39

Min. and max.                -0.99; 0.52
----------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-64-fBodyGyro-std()-Z', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.8, -0.6, -0.4, 
-0.2, 0, 0.2, 0.4), xmax = c(-0.8, -0.6, -0.4, -0.2, 0, 0.2, 
0.4, 0.6), ymin = c(0, 0, 0, 0, 0, 0, 0, 0), ymax = c(90L, 5L, 
37L, 36L, 6L, 4L, 1L, 1L)), .Names = c("xmin", "xmax", "ymin", 
"ymax"), row.names = c(NA, -8L), class = "data.frame"), vnam = "fBodyGyro-std()-Z")
```
</div>
</div>




---

## fBodyAccMag-std()

<div class = "row">
<div class = "col-lg-8">

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Median                             -0.65

1st and 3rd quartiles       -0.95; -0.37

Min. and max.                -0.99; 0.18
----------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-65-fBodyAccMag-std()', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.0999999999999999), xmax = c(-0.9, 
-0.8, -0.7, -0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.0999999999999999, 
0.2), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0), ymax = c(82L, 
6L, 1L, 3L, 13L, 20L, 20L, 8L, 8L, 9L, 7L, 3L)), .Names = c("xmin", 
"xmax", "ymin", "ymax"), row.names = c(NA, -12L), class = "data.frame"), 
    vnam = "fBodyAccMag-std()")
```
</div>
</div>




---

## fBodyBodyAccJerkMag-std()

<div class = "row">
<div class = "col-lg-8">

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Median                             -0.81

1st and 3rd quartiles       -0.98; -0.27

Min. and max.                -0.99; 0.32
----------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-66-fBodyBodyAccJerkMag-std()', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.8, -0.6, -0.4, 
-0.2, 0, 0.2), xmax = c(-0.8, -0.6, -0.4, -0.2, 0, 0.2, 0.4), 
    ymin = c(0, 0, 0, 0, 0, 0, 0), ymax = c(90L, 1L, 25L, 22L, 
    27L, 12L, 3L)), .Names = c("xmin", "xmax", "ymin", "ymax"
), row.names = c(NA, -7L), class = "data.frame"), vnam = "fBodyBodyAccJerkMag-std()")
```
</div>
</div>




---

## fBodyBodyGyroMag-std()

<div class = "row">
<div class = "col-lg-8">

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Median                             -0.77

1st and 3rd quartiles       -0.95; -0.43

Min. and max.                -0.98; 0.24
----------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-67-fBodyBodyGyroMag-std()', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2), xmax = c(-0.9, 
-0.8, -0.7, -0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 
0.3), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0), ymax = c(80L, 
10L, 1L, 6L, 18L, 24L, 23L, 7L, 7L, 2L, 1L, 0L, 1L)), .Names = c("xmin", 
"xmax", "ymin", "ymax"), row.names = c(NA, -13L), class = "data.frame"), 
    vnam = "fBodyBodyGyroMag-std()")
```
</div>
</div>




---

## fBodyBodyGyroJerkMag-std()

<div class = "row">
<div class = "col-lg-8">

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values              180

Median                             -0.89

1st and 3rd quartiles       -0.98; -0.61

Min. and max.                   -1; 0.29
----------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-68-fBodyBodyGyroJerkMag-std()', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.8, -0.6, -0.4, 
-0.2, 0, 0.2), xmax = c(-0.8, -0.6, -0.4, -0.2, 0, 0.2, 0.4), 
    ymin = c(0, 0, 0, 0, 0, 0, 0), ymax = c(94L, 41L, 29L, 10L, 
    5L, 0L, 1L)), .Names = c("xmin", "xmax", "ymin", "ymax"), row.names = c(NA, 
-7L), class = "data.frame"), vnam = "fBodyBodyGyroJerkMag-std()")
```
</div>
</div>




---



Report generation information:

 *  Created by Mandell, Zachary (username: `ZMandell`).

 *  Report creation time: Tue May 07 2019 15:17:29

 *  Report was run from directory: `C:/Users/zmandell/Desktop/Coursera/Cleaning Data - Course 3/Data`

 *  dataMaid v1.2.0 [Pkg: 2018-10-03 from CRAN (R 3.4.4)]

 *  R version 3.4.3 (2017-11-30).

 *  Platform: x86_64-w64-mingw32/x64 (64-bit)(Windows >= 8 x64 (build 9200)).

 *  Function call: `makeDataReport(data = tidy, mode = c("summarize", "visualize", 
"check"), smartNum = FALSE, file = "codebook_tidy.Rmd", checks = list(
    character = "showAllFactorLevels", factor = "showAllFactorLevels", 
    labelled = "showAllFactorLevels", haven_labelled = "showAllFactorLevels", 
    numeric = NULL, integer = NULL, logical = NULL, Date = NULL), 
    listChecks = FALSE, maxProbVals = Inf, codebook = TRUE, reportTitle = "Codebook for tidy")`

